A Survey on Ordered Binary Decision Diagrams

### 2015-09-11 paper.tex
Add reference to Apply pseudocode
Add author to Apply pseudocode reference
Start Compose operation
Fix formula notation to be consistent
Fix node notation to be consistent

As the name suggests, \textit{Reduced} Ordered Binary Decision Diagrams are a 
minimized representation of BDDs. Furthermore, the decision variables are ordered
consistently. More formally, for any node $\upsilon$ and their respective children
$\omega_1$ and $\omega_2$, a total ordering is imposed, i.e.
$var(\upsilon) < var(\omega_1)$ and $var(\upsilon) < var(\omega_2)$, respectively,
where $var(x)$ denotes the label of node $x$~\cite{BRYANT86, BRYANT92}.

@@

\textit{Shannon's expansion} forms the basis of the recursive
algorithm~\cite{BRYANT86}:
\begin{center}
$
f_1\;op\;f_2 =
\overline{x} \cdot \left(f_1|_{x\leftarrow 0}\;op\;f_2|_{x\leftarrow 0}\right)
+ x \cdot \left(f_1|_{x\leftarrow 1}\;op\;f_2|_{x\leftarrow 1}\right)
$
\end{center}

@@

There are some refinements when it comes to implementation. Those are covered in
Section~\ref{sec:implementational-aspects} as well as the original paper of
Bryant~\cite{BRYANT86, BRYANT92}.  However, assuming an efficient implementation,
the time complexity can be bound to
$O\left(|V_{f_1}| \cdot |V_{f_2}|\right)$~\cite{BRYANT86, BRYANT92}. \tbr

@@

>>>>

As the name suggests, \textit{Reduced} Ordered Binary Decision Diagrams are a 
minimized representation of BDDs. Furthermore, the decision variables are ordered
consistently. More formally, for any node $n$ and their respective children $m_1$
and $m_2$, a total ordering is imposed, i.e. $var(n) < var(m_1)$ and
$var(n) < var(m_2)$, respectively, where $var(x)$ denotes the label of node
$x$~\cite{BRYANT86, BRYANT92}.

@@

\textit{Shannon's expansion} forms the basis of the recursive
algorithm~\cite{BRYANT86}:
\begin{center}
$
f_1\;op\;f_2 =
\overline{x} \land \left(f_1|_{x\leftarrow 0}\;op\;f_2|_{x\leftarrow 0}\right)
\lor x \land \left(f_1|_{x\leftarrow 1}\;op\;f_2|_{x\leftarrow 1}\right)
$
\end{center}

@@

There are some refinements when it comes to implementation. Those are covered in
Section~\ref{sec:implementational-aspects} as well as the original paper of
Bryant~\cite{BRYANT86, BRYANT92}.  However, assuming an efficient implementation,
the time complexity can be bound to
$O\left(|V_{f_1}| \cdot |V_{f_2}|\right)$~\cite{BRYANT86, BRYANT92}.

The full pseudocode defined by Bryant can be found in~\cite[p. 685]{BRYANT86}. \tbr

@@

This operation is merely based upon calls to \textit{Apply} and \textit{Restrict}.
Utilizing \textit{Shannon's expansion}, Bryant~\cite{BRYANT86} formulated the
composition of two functions $f_1$ and $f_2$ as
\begin{center}
$
f_1|_{x=f_2}=
f_2 \land f_1|_{x_i=1} \lor \overline{f_2} \land f_1|_{x_i=0}
$
\end{center}\tbr
